---
title: "class12"
author: "Eva Omar"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Prep for docking
We want to produce a protein-only PDB file and a drug only PDB file.
```{r}
library(bio3d)

#download PDB file
get.pdb("1hsg")
```
```{r}
pdb <- read.pdb("1hsg.pdb")
protein <- atom.select(pdb, "protein", value = TRUE)
write.pdb(protein, file = "1hsg_protein.pdb")
protein
```

and for the ligand
```{r}
ligand <- atom.select(pdb, "ligand", value = TRUE)
write.pdb(ligand, file = "1hsg_ligand.pdb")
ligand

```

Section 2: Docking ligands into HIV-1 protease
For this section, we will use the program called Autodock Vina [4]. Autodock Vina is a fast docking program that requires minimal user intervention and is often employed for high- throughput virtual screening. We will run it from the command line.
On Macs you should now be able to run this command and see the associated help for the vina program:~/Downloads/autodock_vina_1_1_2_mac/bin/vina --help

Worked with the code below, had to change directory for text to work
Mayens-MacBook-Pro:~ evaomar$ cd ~/Desktop/Bimm143/BIMM143_git/
Mayens-MacBook-Pro:BIMM143_git evaomar$ ~/Downloads/autodock_vina_1_1_2_mac/bin/vina --config config.txt --log log.txt




Once the run is complete, you should have two new files all.pdbqt, which contains all the docked modes, and log.txt, which contains a table of calculated affinities based on AutoDock Vina's scoring function [4]. The best docked mode, according to AutoDock Vina, is the first entry in all.pdbqt.
2.3 Inspecting your docking results
In order to visualize the docks and compare to the crystal conformation of the ligand we will process the all.pdbqt to a PDB format file that can be loaded into VMD. To do this we will use R and the Bio3D package.

```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

 Q4: Qualitatively, how good are the docks? Is the crystal binding mode reproduced? Is it the best conformation according to AutoDock Vina?
 - 
 
 
To assess the results quantitatively we will calculate the RMSD (root mean square distance)
between each of the docking results and the known crystal structure using the bio3d package. Back in RStudio read the original ligand with added hydrogens that you produced earlier and
use the rmsd() function to compare to your docking results.

```{r}
# res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```

 Q5: Quantitatively how good are the docks? Is the crystal binding mode reproduced within 1Å RMSD for all atoms?
 -
Q6: How would you determine the RMSD for heavy atoms only (i.e. non hydrogen atoms)? HINT: The atom.
-
 
 
 
